An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-11-25 tex/paper.tex
Fixing some LaTeX.
I know it's still temporary but the document compiles now.

Several iterated prisoner's dilemma tournaments have generated much interest,
including Axelrod's original tournaments, two 2004 anniversary tournaments, and
the S&P 2012 tournament following the discovery of zero-determinant strategies.
Subsequent research has spawned an enormous number of papers, but rarely are the
results reproducible. Among well-known tournaments, in only one case is the full
original source code available (Axelrod's second tournament, in FORTRAN); in no
cases is the available code well-documented, easily modifiable, or released
with significant test suites.

To make matters more complicated, often a newly-created strategy is studied in
isolation by opponents chosen by the strategy's creators, and often such
strategies are not sufficiently described to enable reliable recreation
(in the absense of source code), with \cite{slany2007some} being a notable
counter-example. In some cases strategies are revised without updates to their
names or published implementations \cite{li2007design} \cite{li2011engineering}.
As a result, some of the results related to these strategies and tournaments
have not been reliably replicated, and have not met the basic scientific
criterion of falsifiability.

@@

S&P 2012 is fully reproducible; results are unstable (e.g. substituting soft_majo for
hard_majo changes the results).

@@

Plot of memory_depth vs mean score, mean wins?

>>>>

Several iterated prisoner's dilemma tournaments have generated much interest,
including Axelrod's original tournaments, two 2004 anniversary tournaments, and
the Stewart and Plotkin 2012 tournament following the discovery of
zero-determinant strategies.  Subsequent research has spawned an enormous number
of papers, but rarely are the results reproducible. Among well-known
tournaments, in only one case is the full original source code available
(Axelrod's second tournament, in FORTRAN); in no cases is the available code
well-documented, easily modifiable, or released with significant test suites.

To make matters more complicated, often a newly-created strategy is studied in
isolation by opponents chosen by the strategy's creators, and often such
strategies are not sufficiently described to enable reliable recreation
(in the absense of source code), with \cite{slany2007some} being a notable
counter-example. In some cases strategies are revised without updates to their
names or published implementations \cite{li2007design, li2011engineering}.
As a result, some of the results related to these strategies and tournaments
have not been reliably replicated, and have not met the basic scientific
criterion of falsifiability.

@@

Stewart and Plotkin 2012 is fully reproducible; results are unstable (e.g.\
substituting \texttt{soft\_majo} for \texttt{hard\_majo} changes the results).

@@

%Plot of memory_depth vs mean score, mean wins?
